The design and implementation of standards-based Grid single sign-on using federated identity

### 2009-05-01 doc/sec/papers/GRID09/paper.tex
little change

\subsection{Performance of the integration of the SAML2 SSO profile}
\label{sec:perfsaml2sso}
In our next experiment, we evaluate how does the integration of the SAML2SSO
profile affect the performance of Web Service invocation. We configure an ``echoString'' service
together with as SP (Service Provider) service, and develop a client by using
SAML2SSO related API of ARC, to invoke the ``echoString'', as well as interact with the IdP (Identity Provider).
Service and clients run on the same set of machine as Section~\ref{sec:perhedandaxis}. Meanwhile, we deploy
the Shibboleth IdP implementation on a machine equipped with 2.8GHz Intel Pentium CPU and 1GB
memory, Red Hat Enterprise Linux 5. We run Shibboleth IdP (2.0.0) on Apache Tomcat(6.0.18), and
configure the JVM memory for Tomcat by setting ``CATALINA\_OPTS=-Xms16m -Xmx256m''. The Java
version is 1.6.0_07.

@@

In order to improve the performance of SAML2SSO profile, optimizing the process
between client and IdP is the correct direction. Considerting most of the performance 
characteristics for the Shibboleth IdP are determined by the Servlet Container (that is Tomcat 
in our test environment) and Java VM running it, we also increase the JVM memory for Tomcat 
by setting ``CATALINA\_OPTS=-Xms256m -Xmx1024m'', and the performance result after setting
shows little improvement.
Therefore we conclude that the easiest way is to enhance the hardware configuration.

@@

The results show that the throughput of SLCS service has the same characteristic
as the throughput of ``echoString'' service enhanced with SAML2SSO profile, with the value being
around 215 requests per minute; and the average response time is close to the value of
``echoString'' service as well, with the value being increased to about 80ms. The increased time
consumption is caused by the creating of X.509 request (1024-bit RSA key pair generation) on the client
side.

@@

>>>>

\subsection{Performance of the integration of the SAML2 SSO profile}
\label{sec:perfsaml2sso}
In our next experiment, we evaluate how does the integration of the SAML2SSO
profile affect the performance of Web Service invocation. We configure an ``echoString'' service
together with as SP (Service Provider) service, and develop a client by using
SAML2SSO related API of ARC, to invoke the ``echoString'', as well as interact with the IdP (Identity Provider).
Service and clients run on the same set of machine as Section~\ref{sec:perhedandaxis}. Meanwhile, we deploy
the Shibboleth IdP implementation on a machine equipped with 2.8GHz Intel Pentium CPU and 1GB
memory, Red Hat Enterprise Linux 5. We run Shibboleth IdP (2.0.0) on Apache Tomcat(6.0.18), and
configure the JVM memory for Tomcat by setting ``CATALINA\_OPTS=-Xms16m -Xmx256m''. The Java
version is 1.6.0\_07.

@@

In order to improve the performance of SAML2SSO profile, optimizing the process
between client and IdP is the correct direction. Considering most of the performance 
characteristics for the Shibboleth IdP are determined by the Servlet Container (that is Tomcat 
in our test environment) and Java VM running it, we also increase the JVM memory for Tomcat 
by setting ``CATALINA\_OPTS=-Xms256m -Xmx1024m'', and the performance result after setting
shows little improvement in terms of throughput and reponse time.
Therefore we conclude that the easiest way is to enhance the hardware configuration.

@@

The results show that the throughput of SLCS service has the same characteristic
as the throughput of ``echoString'' service enhanced with SAML2SSO profile, with the value being
around 215 requests per minute; and the average response time is close to the value of
``echoString'' service as well, with the value being increased to about 80ms. The increased time
consumption is caused by the creating of X.509 request (1024-bit RSA key pair generation) on the client
side. We conclude that the performance of SLCS service is mostly influenced by the SAML2SSO profile,
while the performance consumption for RSA key pair generation is very little comparing with the 
consumption for SAML2SSO profile.

@@

In the delegation process (showing in Figure~\ref{fig:DelegUML}), the delegation service needs
to generate RSA pair key (step 2 in Figure~\ref{fig:DelegUML}), and the ``echoString'' service
needs to generate RSA pair key (step 10 in Figure~\ref{fig:DelegUML}). Also the delegation service
needs to sign the X.509 request from ``echoString'' service.
We speculate the throughput of ``echoString'' service that configured with credential delegation
is mainly influenced by these cryptographic operations.
